Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-15 Paper_presentation.tex
Tabela redimensionada

\item[\checkmark]

\item[\checkmark]

@@

>>>>

\item[\checkmark]The shared data provide each investigator with a view of CP offenders and a method of triage for selecting targets  (and enable this study).

\item[\checkmark]The tools are still in use, and law enforcement execute approximately 150 search warrants nationwide per month.

@@

\begin{block}{Datasets}

\begin{table}[H]
\begin{small} 
\setlength{\tabcolsep}{0.1pt} 
\centering

\caption{Datasets} 
\label{tab:table1}
\begin{tabular}{|c|c|c|c|c|}\hline \\

Network & Data Range & Files & GUIDs & Records \\

\hline
\hline
Gnutella (FOI only) & 10/1/2010–9/18/2011 & 139,604 & 775,941 & 870,134,671 \\
Gnutella Browse & 6/1/2009–9/18/2011 & 87,506,518 & 570,206 & 434,849,112 \\
eMule (FOI only) & 10/1/2010–9/18/2011 & 29,458 & 1,895,804 & 133,925,130 \\
IRC (no file data) & 6/2/2011–9/18/2011 & N/A & N/A & 7,272,739 \\
Ares (no file data) & 5/31/2011–9/18/2011 & N/A & N/A & 17,706,744\\

\hline
\end{tabular}
\end{small}
\end{table}
